---
title: "Data Science final project R Notebook"
output: html_notebook
---

Try executing this chunk by clicking the *Run* button within the chunk or by placing your cursor inside it and pressing *Cmd+Shift+Enter*. 

```{r}
# initialization
library(ggplot2)

pkgTest <- function(x)
{
  if (!require(x,character.only = TRUE))
  {
    install.packages(x,dep=TRUE)
    if(!require(x,character.only = TRUE)) stop("Package not found")
  }
}

pkgTest("ROCR")

getAUC <- function(preds, obs)
{
  return(attributes(performance(prediction(preds, obs), "auc"))$y.values[[1]])
}
pkgTest("caret")
pkgTest("pROC")

predTest_plot <- function(trained_model, model_name)
{
  print(trained_model)
  tryCatch({
    plot(trained_model)
  }, error = function(e) {
    conditionMessage(e)
  })
  result.predicted.prob <- predict(trained_model, d_test, type="prob") 
  # print(head(result.predicted.prob))
  result.roc <- roc(response = d_test$click_bool, predictor = result.predicted.prob$X2)
  print(paste(model_name, " AUC: ",round(result.roc$auc,3)))
  plot(result.roc, main=paste(model_name, " ROC plot"))
  
  confusionMatrix(data = predict(trained_model, d_test, type="raw"), 
                  reference = d_test$click_bool, positive = "X2")
}
```

```{r}
# load data
# d<-read.csv('./data/smaller_100.csv', header=T,sep=",", na.strings = "NULL")
d<-read.csv('./data/s.csv', header=T, sep=",", na.strings = "NULL")
# summary(d)
print(nrow(d))
varNames <- names(d)
```
```{r}
# visualize missing value
missing <- data.frame(matrix(NA, nrow=54, ncol=2))
for(i in 1:dim(d)[2]){
	# calcaulate the missing number
	missing[i,2] <- sum(is.na(d[,i]))/nrow(d)
}
missing[,1] <- colnames(d)
names(missing) <- c('names','percentage')
ggplot(missing, aes(x=reorder(names, percentage), y=percentage)) +geom_bar(stat='identity') + theme(axis.text.x = element_text(angle = 90, hjust = 1)) + ylab("Missing Value Percentage")

```


```{r}
# data preprosessing: deal with missing value
# fill worst case of hotel missing value, review, location_score
d$prop_review_score[is.na(d$prop_review_score)] <- 0
d$prop_location_score2[is.na(d$prop_location_score2)] <- 0
min_srch_score <- range(d$srch_query_affinity_score, na.rm=T)[1]
d$srch_query_affinity_score[is.na(d$srch_query_affinity_score)] <- min_srch_score

## competitor information
for(i in seq(28,51, by=1)){
	d[is.na(d[,i]), i] <- 0
}

# drop columns
d$gross_bookings_usd <- NULL
d$date_time <- NULL

# for NAs of users' historical data,
# we replace them by the mean value of the column
avg_v_usd <- mean(d$visitor_hist_adr_usd, na.rm=T)
avg_v_star <- mean(d$visitor_hist_starrating, na.rm=T)
d$visitor_hist_adr_usd[is.na(d$visitor_hist_adr_usd)] <- avg_v_usd
d$visitor_hist_starrating[is.na(d$visitor_hist_starrating)] <- avg_v_star
avg_dis <- mean(d$orig_destination_distance, na.rm=T)
d$orig_destination_distance[is.na(d$orig_destination_distance)] <- avg_dis

# log price
ggplot(d, aes(x=d$price_usd)) + geom_histogram(col = 'white') + theme_light()
d$price_usd <- log(d$price_usd)
d$visitor_hist_adr_usd <- log(d$visitor_hist_adr_usd)
ggplot(d, aes(x=log(d$price_usd+1))) + geom_histogram(col = 'white') + theme_light()

# check any NA left or not: should be 0.
print(sum(is.na(d)))

# original:integer, need to be factor for classification
d$click_bool <- factor(d$click_bool)

# convert format for caret: X1, X2
levels <- unique(c(d[["click_bool"]]))
d[["click_bool"]] <- factor(d[["click_bool"]],
              labels=make.names(levels))
table(d$click_bool)
```

```{r}
# split data into train and test
smp_size <- floor(0.75 * nrow(d))
set.seed(5566)
train_ind <- sample(seq_len(nrow(d)), size = smp_size)
d_train <- d[train_ind, ]
d_test <- d[-train_ind, ]
nrow(d_train)
```

```{r}
# use subset data, srch_id % 100 equal 8
ori_num <- nrow(d_train)
# d <- subset(d, as.numeric(d$srch_id)%%10==8)
# balance data(undersampling)
pos_num <- sum(d_train$click_bool=='X2')
d_sub <- d_train[sample(nrow(d_train), size=round(pos_num*1.02,0), replace=FALSE),]
d_train <- rbind(subset(d_train, d_train$click_bool=='X2'), d_sub)
# sum(d_balance$click_bool=='1')
print(paste(round(nrow(d_train)/ori_num*100,3), "% data left."))
```


```{r}
# show numbers of clicking and unclicking
# round(prop.table(table(d$click_bool)),4)
table(d$click_bool)
total_rows <- nrow(d)
num_positive <- table(d$click_bool)[2]
print(paste("Ratio of click of all search results:", round(num_positive/total_rows*100,2),"%"))

# show relation between position and booking
clickData<-d[which(d$click_bool=="X2"),]
summary(d$position)
table(d$click_bool,d$position)
print(qplot(position, data=clickData, geom="histogram", binwidth=1, main = "# of clicking vs Position "))
# note that at position 5, 11 ,..there are fewer data.
```


```{r}
# calculate AUC and draw ROC of null model 1: all prediction = 0, AUC = 0.5
pred.0 <- rep(0,nrow(d))
getAUC(pred.0, d$click_bool)
pred1 <- prediction(pred.0, d$click_bool)
perf1 <- performance(pred1, "tpr", "fpr")
plot(perf1)

#null model 2: position and desicion tree
# dt.model <- rpart("click_bool ~ position + price_usd ", data=d_train)
set.seed(1234)
train_contrl <- trainControl(method = "cv", number = 5, summaryFunction=twoClassSummary, classProbs=T)
dt.model <- train(as.formula(paste("click_bool", "position", sep = " ~ ")), data=d_train, method="rpart", metric="ROC", trControl=train_contrl)
predTest_plot(dt.model, "Decision tree")
```

```{r}
# Features selection
# varNames1 <- c("position", "prop_review_score")
varNames1 <- varNames[!varNames %in% c("click_bool","date_time", "gross_bookings_usd", "booking_bool")]
# do not use competitor information
varNames1 <- varNames1[!grepl("comp",varNames1 )]
varNames1 <- paste(varNames1, collapse = "+")
feat.form <- as.formula(paste("click_bool", varNames1, sep = " ~ "))
print(feat.form)
```


```{r}
# apply random forest
pkgTest("randomForest")
set.seed(119)
rf.fit <- randomForest(feat.form, d_train, importance=T, ntree=50, na.action = na.exclude)
plot(rf.fit)
varImpPlot(rf.fit, sort = T)
```

```{r}
# caret random forest model, and CV, AUC
start.time <- Sys.time()
train_contrl <- trainControl(method = "cv", number = 5, summaryFunction=twoClassSummary, classProbs=T)
rf.model <- train(feat.form, data = d_train, method="rf", trControl=train_contrl, metric="ROC")
end.time <- Sys.time()
print(paste("Random Forest training time:", round(end.time - start.time,2), 
            'seconds'))
# Predict and calculate AUC and draw ROC curve.
predTest_plot(rf.model, "Random Forest")
```

```{r}
# Model: logistic regression
start.time <- Sys.time()
train_contrl <- trainControl(method = "cv", number = 5, summaryFunction=twoClassSummary, classProbs=T)
lr.model <- train(feat.form, data = d_train, method="glm", trControl=train_contrl, metric="ROC")
end.time <- Sys.time()
print(paste("Logistic Regression training time:", round(end.time - start.time,2), 
            'seconds'))
# Predict and calculate AUC and draw ROC curve.
predTest_plot(lr.model, "Logistic Regression")
```

```{r}
# use SVM model
set.seed(1492)
start.time <- Sys.time()
train_contrl <- trainControl(method = "cv", number = 5, summaryFunction=twoClassSummary, classProbs=T)
svm.model <- train(feat.form, d_train, method = "svmRadial", tuneLength = 9,metric="ROC", trControl=train_contrl)
end.time <- Sys.time()
print(paste("SVM training time:", round(end.time - start.time,2), 
            'seconds'))
print(svm.model)
plot(svm.model)
result.predicted.prob <- predict(svm.model, d_test, type="prob") 
result.roc <- roc(response = d_test$click_bool, predictor = result.predicted.prob$X2)
print(paste("SVM with radial kernel AUC: ",round(result.roc$auc,3)))
plot(result.roc, main="ROC plot")

```

```{r}
# Ada boost model:
pkgTest("fastAdaboost")
start.time <- Sys.time()
train_contrl <- trainControl(method = "cv", number = 5, summaryFunction=twoClassSummary, classProbs=T)
ada.model <- train(feat.form, d_train, method = "adaboost", metric="ROC", trControl=train_contrl)
end.time <- Sys.time()
print(paste("Ada boost training time:", round(end.time - start.time,2), 
            'seconds'))
print(ada.model)
plot(ada.model)
result.predicted.prob <- predict(ada.model, d_test, type="prob") 
result.roc <- roc(response = d_test$click_bool, predictor = result.predicted.prob$X2)
print(paste("Ada boost AUC: ",round(result.roc$auc,3)))
plot(result.roc, main="ROC plot")
```

```{r}
# use model xgb
pkgTest("xgboost")
start.time <- Sys.time()
train_contrl <- trainControl(method = "cv", number = 5, summaryFunction=twoClassSummary, classProbs=T)
xgb.model <- train(feat.form, d_train, method='xgbTree', metric="ROC", trControl=train_contrl, nthread =3)
end.time <- Sys.time()
print(paste("XGBtree training time:", round(end.time - start.time,2), 
            'seconds'))
predTest_plot(xgb.model, "XGB tree")
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file).
