---
title: "Data Science R Notebook"
output: html_notebook
---

Try executing this chunk by clicking the *Run* button within the chunk or by placing your cursor inside it and pressing *Cmd+Shift+Enter*. 

```{r}
library(ggplot2)
```

```{r}
d<-read.table('./data/smaller_100.csv', header=T,sep=",")
# d<-read.csv('./data/s.csv', header=T,sep=",")
summary(d)
# typeof(d)
```
```{r}
table(d$click_bool)
round(prop.table(table(d$click_bool)),4)
```



```{r}
# show numbers of non-booking and booking
table(d$booking_bool)
total_rows <- nrow(d)
num_positive <- table(d$booking_bool)[2]
print(paste("Ratio of booking of all search results:", round(num_positive/total_rows*100,2),"%"))
```

```{r}
# show relation between position and booking
# table(d$position,d$booking_bool)
summary(d$position)
table(d$booking_bool,d$position)
print(qplot(position, data=bookingData, geom="histogram", binwidth=1, main = "# of Bookings vs Position "))
# note that at position 5, 11 ,..there are fewer data.
```


Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file).
